\begin{abstract}

SD-TMSR 2,250 MWth is a Single-fluid Double-zone Thorium-based Molten Salt Reactor. The active core of this reactor is divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes), in order to improve the Th-U breeding performance. The lack of computational codes which deal with MSR cores stands against developing such a concept. Here, Serpent 2 Monte Carlo code has been adopted to analyze the whole core model of the SD-TMSR with online reprocessing and refueling. 
In the steady state calculations, molten salt with composition: LiF-BeF2-ThF4-233UF4 at 70-17.5-12.3-0.2 mole\%, respectively is used, this leading to $K_{ef}f = 1.00055\pm0.00089$. The breeding ratio (BR) calculated by the Serpent 2 code in the steady state is $1.11604\pm 0.00033$. The molten salt Temperature Coefficient of Reactivity (TCR) found to be negative and equal to -3.13 pcm/K. In addition, the variation of multiplication factor, BR and build-up of the important nuclides in the core as a function of burnup time have been investigated. Under online reprocessing and refueling, the multiplication factor is increased from $1.00055\pm0.00089$ to $1.10473\pm0.00082$ over 60 years. When the chemical reprocessing rate is 5 m$^3$/d, the reactor can operate as an iso-breeding.
In conclusion, the full core of SD-TMSR has been modeled and the net production of 233U is found to be positive and linearly proportional to the burnup time. The net production of 233U reached 4.25 tons at the end of the period.

\end{abstract}


